---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regexciteklv

<!-- badges: start -->
<!-- badges: end -->

The goal of regexciteklv is to make regular expressions more exciting!
It provides convenience functions to make some common tasks with string manipulation and regular expressions a bit easier.

## Installation

You can install the development version of regexciteklv from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Kingslin0810/regexciteklv")
```
## Usage

A fairly common task when dealing with strings is the need to split a single string into many parts.
This is what `base::strplit()` and `stringr::str_split()` do.

```{r}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(regexciteklv)
str_split_one(x, pattern = ",")
```

